Tutorial 1a

### 2025-07-08 Tutorial_1a.Rmd
update Figure 2 (differently shaped points)

To set up a life table, the user has to supply both a width in ms for the time bins, and a censoring time, the last time point for which the trials are considered under investigation (a cutoff time, or timeout; the response deadline). The goal is to find the optimal bin width and censoring time (both in ms) to portray the effects of interest. Note that all response times must be positive.

>>>>

To set up a life table, the user has to supply both a width in ms for the time bins, and a censoring time, the last time point for which the trials are considered under investigation (a cutoff time, or timeout; the response deadline if one is used). The goal is to find a good bin width and censoring time (both in ms) to portray the effects of interest. Note that all response times must be positive.
